Usage metrics

### 2021-03-08 analysis/usage.Rmd
Fix number of language expression for Kaggle

---
title: "Usage metrics"
author: "Pierre Donat-Bouillud"
output:
    html_document:
        gallery: false
        toc: true
        toc_depth: 3
        toc_float: true
        df_print: paged
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: Data/kaggle/
  calls_path: summarized.fst
  corpus_path: ../corpus.fst
  static_path: evals-static.csv
  force_rebuild: TRUE
---

@@

```{r read, message=TRUE, include=F}
read_fst(corpus_path) %>% as_tibble() -> C_raw

@@

```{r coverage-per-package}
cov_packages <- static_call_sites_per_package %>%
  left_join(sites_per_package, by = c("package" = "ev_package"), suffix = c("_static", "_tracer")) %>% 
  mutate(n_tracer = replace_na(n_tracer, 0L))

# if n_static < n_tracer, adjust n_tracer to n_static
# Probably due to higher-order functions taking some eval
cov_packages <- cov_packages %>%
  mutate(n_static_c = if_else(n_static < n_tracer, n_tracer, n_static))

cov_packages <- cov_packages %>% mutate(coverage = 100 * n_tracer / n_static_c)

cov_packages %>% ggplot() +
  geom_histogram(aes(x = coverage), binwidth=1) + 
  labs(x = "coverage (%)")

ggsave(path(PLOT_DIR, "coverage_per_package.pdf"))
```

What is the actual coverage vs the expected coverage?
```{r}
corpus_cov<- C_raw %>% select(package, size, revdeps)

corpus_cov<- corpus_cov %>% left_join(cov_packages, by = "package") %>%
  mutate(revdeps = replace_na(revdeps, 0))

corpus_cov %>% ggplot() +
  geom_point(aes(x = coverage, y = revdeps, size = size)) + 
  scale_y_log10() +
  scale_size_area() +
  labs(x = "coverage (%)", y = "Reverse dependencies")

ggsave(path(PLOT_DIR, "coverage_per_package_size.pdf"))
```

```{r}
corpus_cov %>% ggplot() +
  geom_point(aes(x = coverage, y = revdeps, size = n_static)) + 
  scale_y_log10() +
  scale_size_area() +
  labs(x = "coverage (%)", y = "Reverse dependencies", size = "Static call sites")

ggsave(path(PLOT_DIR, "coverage_per_package_static_call_sites.pdf"))
```

@@

symbs <- types %>% filter(type == "symbol") %>% .$n
languages <- types %>% filter(type == "language") %>% .$n
expressions <- types %>% filter(type == "expression") %>% .$n

>>>>

---
title: "Usage metrics"
author: "Pierre Donat-Bouillud"
output:
    html_document:
        gallery: false
        toc: true
        toc_depth: 3
        toc_float: true
        df_print: paged
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: Data/kaggle/
  calls_path: summarized.fst
  corpus_path: corpus.txt
  static_path: evals-static.csv
  force_rebuild: TRUE
---

@@

```{r read, message=TRUE, include=F}
tibble(package = read_lines(corpus_path)) -> C_raw

@@

@@

symbs <- types %>% filter(type == "symbol") %>% .$n
languages <- types %>% filter(type == "language") 
languages <- if(nrow(languages) == 0) 0 else languages$n

expressions <- types %>% filter(type == "expression") %>% .$n
